Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-08 papers/ms.tex
paper: add plots of spectra

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f5a.pdf}
			\includegraphics[width=0.49\textwidth]{f5b.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Lithium 6708\AA\ equivalent widths for Kepler-1643, KOI-7368,
    KOI-7913 AB, and Kepler-1627 compared to those of young open
    clusters and field stars. }
    The statistical uncertainties on the newly measured equivalent
    widths are shown, or else are smaller than the markers.
    The field stars are stars with Kepler planets from \citet{berger_identifying_2018}.
    The ``40-50 Myr'' reference stars (left) are from
		IC\,2602 \citep{randich_gaiaeso_2018} and Tuc-Hor
		\citep{kraus_stellar_2014}.
    The ``112 Myr'' stars (right) are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018},
    where we adopt the LDB age from \citet{dahm_2015}.
    \label{fig:lithium}
	}
\end{figure*}

@@

Figure~\ref{fig:lithium} compares the measured lithium equivalent
widths of the objects of interest against a few reference populations.
We selected the reference populations from the literature only for
cases in which upper limits were explicitly reported.  KOI-7368 and
KOI-7913~A have secure lithium detections, and the KOI-7913~B
detection is marginal (${\rm EW}_{\rm Li} = 42^{+12}_{-19}$).  For all
three stars, as well as for Kepler-1627~A, the observed lithium
equivalent width is consistent with the stellar effective temperatures
and $\approx40$\,Myr ages.

@@

One explanation for this could be that Kepler-1643 is a field
interloper; another could be that RSG-5 is older than 50\,Myr.  We do
not favor the former, given that {\it i)} the star was selected based
on its spatio-kinematic proximity to other RSG-5 members, nearly all
of which appear consistent with being $\approx$50\,Myr old
(Figure~\ref{fig:age} upper left), and {\it ii)} the same RSG-5
members display a gyrochronal sequence consistent with being younger
than the Pleaides (Figure~\ref{fig:age} lower left).
We do not have an explanation, but in the following paragraph
speculate on one possible line of thinking that might help resolve the
discrepancy.

>>>>

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Key spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown as in the observed frame, and
    the stars are sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

Figure~\ref{fig:koiyouthindicators} shows key portions of the HIRES
and TRES spectra for the Kepler objects in Cep-Her.
Lithium absorption is obvious at 6708\AA\ in all stars except KOI-7913 B, where it is marginal.
H$\alpha$ is in emission for both components of KOI-7913,
and in absorption for the hotter stars.
In the following, 
we compare these observations against stars in benchmark
open clusters.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
			\includegraphics[width=0.49\textwidth]{f6b.pdf}
		}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Lithium 6708\AA\ equivalent widths for Kepler-1643, KOI-7368,
    KOI-7913 AB, and Kepler-1627 compared to those of young open
    clusters and field stars. }
    The statistical uncertainties on the newly measured equivalent
    widths are shown, or else are smaller than the markers.
    The field stars are stars with Kepler planets from \citet{berger_identifying_2018}.
    The ``40-50 Myr'' reference stars (left) are from
		IC\,2602 \citep{randich_gaiaeso_2018} and Tuc-Hor
		\citep{kraus_stellar_2014}.
    The ``112 Myr'' stars (right) are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018},
    where we adopt the LDB age from \citet{dahm_2015}.
    \label{fig:lithium}
	}
\end{figure*}

Figure~\ref{fig:lithium} compares the measured lithium equivalent
widths of the Kepler objects against a few reference populations.
We selected studies from the literature only where
upper limits were explicitly reported.  KOI-7368 and
KOI-7913~A have secure lithium detections, and the KOI-7913~B
detection is marginal (${\rm EW}_{\rm Li} = 42^{+12}_{-19}$).  For all
three stars, as well as for Kepler-1627~A, the observed lithium
equivalent width is consistent with the stellar effective temperatures
and $\approx40$\,Myr ages.

@@

One explanation for this could be that Kepler-1643 is a field
interloper; another could be that RSG-5 is older than 50\,Myr.  We do
not favor the former, given that {\it i)} the star was selected based
on its spatio-kinematic proximity to other RSG-5 members, nearly all
of which appear consistent with being $\approx$50\,Myr old
(Figure~\ref{fig:age} upper left), and {\it ii)} the same RSG-5
members display a gyrochronal sequence consistent with being younger
than the Pleaides (Figure~\ref{fig:age} lower left).
We do not have an explanation, but in the following paragraph
speculate on one possible line of future work that might help resolve the
discrepancy.
